Paper Two

### 2023-02-22 Paper Two .qmd
minor changes

#plot1
pm10%>%group_by(Country)%>%
  ggplot(aes(x=Country , y=pm10$`PM10 Annual mean, ug/m3`,  fill=Country)) + 
    coord_flip() +
    geom_bar(stat="identity", width=.90) + 
    xlab("") + # Set axis labels
    ylab("") + 
    guides(fill=FALSE) +
    ggtitle("Number of Turbine Manufacturers by Country")
#plot2
ggplot(pm10, aes(x=Year , y=`PM10 Annual mean, ug/m3`)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  geom_smooth(method = "loess", se = FALSE, color = "red") +
  geom_text(aes(label = Country), hjust = -0.2, vjust = 1.2, size = 1.5)+
  theme_minimal()
```

>>>>

#plot1
pm10%>%group_by(Country)%>%
  ggplot(aes(x=Country , y=pm10$`PM10 Annual mean, ug/m3`,  fill=Country)) + 
    coord_flip() +
    geom_bar(stat="identity", width=.90) + 
    xlab("") + # Set axis labels
    ylab("") + 
    guides(fill=FALSE) +
    ggtitle("Number of Turbine Manufacturers by Country")

#plot2
ggplot(pm10, aes(x=Year , y=`PM10 Annual mean, ug/m3`)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  geom_smooth(method = "loess", se = FALSE, color = "red") +
  geom_text(aes(label = Country), hjust = -0.2, vjust = 1.2, size = 1.5)+
  theme_minimal()
```
